Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 Discussion-Proof.tex
fix to thm 9
addressed Theorem 10 when L=0

\begin{rtheorem}{Theorem}{\ref{rst:discrete}}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment budget bounded above by 
\begin{align*}
\pfedit{
O \left(\ARMNUM^2  d^{7/2} D^{5/2} \sigma^{5/2} \cdot (\MAXR + \Diam d \sigma)\cdot
    \max\bigg\{
    \frac{1}{\TieCutoff},
    \frac{\TieDensity}{\MinProb} \bigg\}^{5/2}
\right)
}
\end{align*}
and expected regret bounded above by 
\begin{align}
O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
  \right).  \nonumber
\end{align}
\end{rtheorem}

\begin{proof}
The proof of the expected payment bound is the same as the proof of Theorem~\ref{rst:budget}, except that we now define $h(\ell) := \max \left( \frac{2}{\MinProb},
\pfedit{
\left( \frac{24 \sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
}
\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
\right)$.

To prove the bound on the expected regret, one can first prove tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
which replace the $\exp(2/\MinProb)$ term with simply $2/\MinProb$.
In return, the length of phase $s$ is now bounded only be $\ARMNUM s$ instead of $\ARMNUM \log(s)$.
Substituting these changes into the proof\pfedit{s} of Theorem\pfedit{s}~\ref{rst:regret} \pfedit{and \ref{rst:budget}}, we obtain the claimed bounds.

\pfcomment{
The calculation I did for the bound on the expected payment is,
\begin{align*}
&O \left(\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma) \cdot h(1) \right) \\ 
&=O \left(\ARMNUM^2  d \cdot (\MAXR + \Diam d \sigma)\cdot
    \max\bigg\{\frac{2}{p},
    \left( \frac{\sigma \Diam d}{\TieCutoff} \right)^{5/2},
    \left( \frac{\sigma \TieDensity \Diam d}{\MinProb} \right)^{5/2}\bigg\}
\right)\\
&=O \left(\ARMNUM^2  d^{7/2} D^{5/2} \sigma^{5/2} \cdot (\MAXR + \Diam d \sigma)\cdot
    \max\bigg\{
    \frac{1}{\TieCutoff},
    \frac{\TieDensity}{\MinProb} \bigg\}^{5/2}
\right).
\end{align*}
}

\end{proof}

@@

\begin{rtheorem}{Theorem}{\ref{rst:known-p}}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment budget bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
\end{align*}
and an expected regret bounded above by
\bcedit{
\begin{align*}
O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
  + \frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
\end{align*}
}
\end{rtheorem}

\begin{proof}
  The proof of the expected payment bound follows Lemma~\ref{rst:budget} except for defining
  $h(\ell) := \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}$
(without including the $\exp(2/\MinProb)$ term).

>>>>

\begin{rtheorem}{Theorem}{\ref{rst:discrete}}
Under Assumption~\ref{a:discrete}, the Discrete-Preference Algorithm has expected payment budget bounded above by 
\begin{align*}
O \left(\frac{\ARMNUM^2 d \cdot (\MAXR + \Diam d \sigma)\sigma^{5/2}L^{5/2}\Diam^{5/2}d^{5/2}}{\MinProb^{5/2}} \right),
\end{align*}
and expected regret bounded above by 
\begin{align}
O \left(\MAXR\cdot \frac{\ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
  \right).  \nonumber
\end{align}
\end{rtheorem}

\begin{proof}
The proof of the expected payment bound is the same as the proof of Theorem~\ref{rst:budget}, except that we now define $h(\ell) := \max \left( \frac{2}{\MinProb},
\left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}
\right)$.

To prove the bound on the expected regret, one can first prove tightened versions of Lemmas~\ref{lem:no-incentives} and \ref{lem:numP},
which replace the $\exp(2/\MinProb)$ term with simply $2/\MinProb$.
In return, the length of phase $s$ is now bounded only be $\ARMNUM s$ instead of $\ARMNUM \log(s)$.
Substituting these changes into the proof of Theorem~\ref{rst:regret}, we obtain the claimed bounds.
\end{proof}

@@

\begin{rtheorem}{Theorem}{\ref{rst:known-p}}
Under Assumption~\ref{a:known-p}, the Known-\MinProb Algorithm has an expected payment budget bounded above by 
    \bcedit{
\begin{align*}
    O\left(\ARMNUM^2 d\cdot(R+Dd\sigma)\cdot \max\bigg\{ \left(\frac{24\sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
        \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}\bigg\}\right)
\end{align*}
}
and an expected regret bounded above by
\bcedit{
\begin{align*}
O \left(\frac{\MAXR \ARMNUM \TieDensity^3 \Diam^3 d^3 \sigma^3}{\MinProb^3}
  + \frac{\MAXR \ARMNUM^2 d^3 \TieDensity^2 \Diam^2 \sigma^2}{\MinProb^2}
  + \frac{\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3}{\MinProb}\right).
\end{align*}
}
\end{rtheorem}

\begin{proof}
  The proof of the expected payment bound follows Lemma~\ref{rst:budget} except for defining
    \bcedit{
    $h(\ell) := \max\big\{ \left(\frac{24\sigma \ell \Diam d}{\TieCutoff} \right)^{5/2},
        \left( \frac{48 \sigma \ell \TieDensity \Diam d}{\MinProb} \right)^{5/2}\big\}$
    }
(without including the $\exp(2/\MinProb)$ term).
